Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-07-13 lqg-strings.tex
added the explicit decomposotion of the expanded Polyakov-Poincare action

Let us write down the gauged Polyakov action for the Poincaré lie algebra valued connection $\mc{A}_a$ whose components are given in \eqref{eqn:poincare-lie-algeba}:
\begin{equation}\label{eqn:poincare-polyakov}
	S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B \eta_{AB},
\end{equation}
where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \eqref{eqn:enlarged-Xs}) and $\eta_{AB}$ is the flat metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \eqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
\begin{equation}\label{eqn:covariant-deriv-v2}
	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + k \mc{A}_{a}^A{}_B X^B.
\end{equation}
Now, we will expand out the action \eqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately. It is clear that the resulting expression will be sum of three terms, with the first term being the (gauged) Polyakov action for the string on $\mb{\Gamma}$, terms describing the coupling of the string on $\mb{\Gamma}$ with fluctuations along the extra dimensions $X^r$ and finally a Polyakov like term for the lone extra dimension. We can write this schematically as:
\begin{equation}\label{eqn:poincare-polyakov-decomp}
	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r].
\end{equation}
One can now argue along the same lines as the original arguments which led to the discovery of D-branes \cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background} to say that the extra dimension $X^r$ will become dynamical in the full theory even though it began life only as a classical constraint on the string worldsheet's location. This will imply that while most of the time the string will remain confined to $\mb{\Gamma}$, fluctuations along $X^r$ can cause the string to leave the ``brane'' and venture out into the bulk $\mb{M}$. If this is truly the case then the geometry of the enlarged bulk $\mb{M}$ will be essential for a description of the full string dynamics.

>>>>

Let us write down the gauged Polyakov action for the Poincaré lie algebra valued connection $\mc{A}_a$ whose components are given in \eqref{eqn:poincare-lie-algeba}:
\begin{equation}\label{eqn:poincare-polyakov}
	S'_{P} = -\frac{T}{2} \int \diff^2 x \sqrt{-g} g^{ab} \mc{D}_a X^A \mc{D}_b X^B G_{AB},
\end{equation}
where now the $X^A = \{X^\mu, X^r\}$ (as mentioned previously in \eqref{eqn:enlarged-Xs}) and $G_{AB}$ is the expanded metric on the $d+2$ enlarged bulk manifold $\mb{M}$ and the covariant derivative is of the form defined in \eqref{eqn:covariant-deriv-v1}, but only now acting on $X^A$ instead of on $X^\mu$:
\begin{equation}\label{eqn:covariant-deriv-v2}
	\mc{D}_a X^A(\tau , \sigma) = \partial_a X^A + k \mc{A}_{a}^A{}_B X^B.
\end{equation}
Now, we will expand out the action \eqref{eqn:poincare-polyakov} and express it in terms of the $X^\mu$ and $X^r$ separately. It is clear that the resulting expression will be sum of three terms, with the first term being the (gauged) Polyakov action for the string on $\mb{\Gamma}$, terms describing the coupling of the string on $\mb{\Gamma}$ with fluctuations along the extra dimensions $X^r$ and finally a Polyakov like term for the lone extra dimension. We can write this schematically as:
\begin{equation}\label{eqn:poincare-polyakov-decomp}
	S'_P[X^A] = S_P[X^\mu] + S_{int}[X^\mu, X^r] + S_P[X^r] ,
\end{equation}
or more explicitly as
\begin{multline} \label{eqn:poincare-polyakov-decomp-explicit}
	S' _{P} [X^{\mu} , X^{r}] = -\frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{\nu} \eta _{\mu \nu} - \\
	- T \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{\mu} \mc{D}_{b} X^{r} G_{\mu r} - \\
	- \frac{T}{2} \int \diff ^2 x \sqrt{- g} g^{a b} \mc{D}_{a} X^{r} \mc{D}_{b} X^{r} G_{r r} ,
\end{multline}
where we can see a natural decomposition of the expanded bulk metric $G_{A B}$ as a $(d+1)$-dimensional tensor $\eta _{\mu \nu}$, a $(d+1)$-dimensional vector $V_{\mu} = G_{\mu r}$ and a scalar $V = G_{r r}$, akin to the ADM decomposition of the metric in standard GR literature.

One can now argue along the same lines as the original arguments which led to the discovery of D-branes \cite{Dai1989New-Connections,Polchinski1995Dirichlet-Branes,Horava1989Background} to say that the extra dimension $X^r$ will become dynamical in the full theory even though it began life only as a classical constraint on the string worldsheet's location. This will imply that while most of the time the string will remain confined to $\mb{\Gamma}$, fluctuations along $X^r$ can cause the string to leave the ``brane'' and venture out into the bulk $\mb{M}$. If this is truly the case then the geometry of the enlarged bulk $\mb{M}$ will be essential for a description of the full string dynamics.
